; AlifeGuard inventory policy. Per-category ceilings for the Inventory Guard scanner
; (ag_inventory_guard.script). Cull releases items above max in each category. Single-value
; rows: "<category> = <max>". DLTX-overridable. Shape parsed by xinventory.load_policy.
; A row keyed by an item section (e.g. grenade_smoke) overrides the category for that section:
; it counts and caps on its own, so grenade_smoke = 0 culls all smoke while grenade = 3 still
; caps other grenades at 3.
;
; Ammo categories count in ROUNDS; other categories count in items. Combat ammo caps at the
; 3-box CAP (45 rifle / 48 pistol; box_size 15 / 16). Sentinel categories (untouchable,
; equipped) are pre-filtered by xinventory and never reach this policy. Item-level runtime
; protections (story_id, companion-gifted, player-strapped) also gate via
; xinventory.get_category.

[ag_inventory_policy]
medkit            = 5
bandage           = 5
antirad           = 3
stim              = 3
pill              = 3
food              = 5
drink             = 3
grenade           = 3
grenade_smoke     = 0      ; cull all: engine crash when NPCs throw smoke grenades
grenade_ammo      = 3
ammo_slot_2_t1    = 48     ; pistol basic, 3 boxes (16/box)
ammo_slot_2_t2    = 48     ; pistol AP
ammo_slot_3_t1    = 45     ; rifle basic, 3 boxes (15/box)
ammo_slot_3_t2    = 45     ; rifle AP
ammo_not_equipped = 0
weapon            = 1
outfit            = 1
helmet            = 1
artefact          = 3
device            = 1
crafting          = 3
other             = 3

; "money" intentionally absent: cull's on_surplus is release_item, which would destroy
; money pile items (kind=i_money pickups). Rare in NPC inventory but safer to leave a
; no-rule = keep gap than risk destruction.
